\texttt{skater}: An R package for SNP-based Kinship Analysis and Benchmarking

### 2021-07-12 paper/paper.Rmd
copy vignette to paper supplementary materials #50 #48

>>>>

```{r, echo=FALSE, eval=FALSE}
## Run this chunk interactively if you update the package vignette.
## This renders the vignette as a PDF with a new title.

# Where is the package vignette?
vpath <- here::here("vignettes/basic_usage.Rmd")
# Where do you want to save the new modified vignette rmarkdown?
spath <- here::here("paper/supplement-vignette.Rmd")
# Read in the vignette rmarkdown text
vtext <- readLines(vpath)
# Create the supplemental material rmarkdown by replacing the title YAML
stext <- sub(pattern='title: "Basic Usage"', 
             replacement = 'title: |\n    | Supplementary Material for:\n    | skater: An R package for SNP-based Kinship Analysis, Testing, and Evaluation\n    | _(skater v0.1.0 package vignette)_', 
             x=vtext)
# Write out that modified yaml to the supplementary material rmarkdown
writeLines(text=stext, con=spath)
# Render it to PDF
rmarkdown::render(spath, output_format="pdf_document")
```
